### 2012-05-22 docs/unit_tests/unit_tests.tex
add a description of test_react

>>>>

\section{\tt test\_react}

  This simply tests the reaction network by calling the \maestro\ {\tt
  react\_state} routine directly.  The network is selected in the {\tt
  GNUmakefile} by setting the {\tt NETWORK\_DIR} variable.  A 3d cube
  is setup with density varying on one axis, temperature varying on
  another, and the composition varying on the third.  The density and
  temperature ranges are set in the inputs file.  The composition is
  read in via an input file.

  A good use of this test is to test whether a burner is threadsafe.
  This is accomplished by compiling with OpenMP (setting {\tt OMP=t})
  and the running with 1 thread and multiple threads (this can be done
  by setting the environment variable {\tt OMP\_NUM\_THREADS} to the 
  desired number of threads).  Since each zone is independent of the
  others, the results should be identical regardless of the number
  of threads.  This can be confirmed using the {\tt fcompare} tool
  in {\tt AmrPostprocessing}.
